\section{Introduction}
\IEEEPARstart{T}{oday}, many companies are using coupons to attract customers and increase their sales. With the rapid growth of online
shopping and e-commerce in recent years, coupon web applications are becoming increasingly more popular and important to reach a wider audience. Because of the large number of existing coupons, it is becoming more difficult for consumers to keep track. Therefore, it is important to provide an effective search method for users.

In our project, we want to investigate the effectiveness of different searching methods through the attributes of the coupons that are stored in a database. We want to compare the performance of relational and non-relational database management systems in terms of response times. Our research question is: Are there measurable and noticeable differences in different methods of searching through the coupons attributes inside the database, and what method performs the best? In terms of response times, is a relational or non-relational database the best option?

For our implementation of the coupon web application, we will be using the Python-based web framework Django and the Google Cloud Platform. Furthermore, we will collect data on the response times of different search methods and database management systems. Afterward, we will analyze the results to determine which method performs the best. With this project, we want to identify the most effective search methods, and how to optimize database performance in web applications.

In the following sections of this report, we will provide a review of the relevant literature, our prototype’s system architecture, present our results, and discuss our measurements and findings.