\section{Preliminary or Related Works}
In this section, related work is presented. Our Project is inspired by the Mydealz web application \cite{Mydealz:2023} and we will implement a lightweight version of this application. Mydealz is an online platform where users can post and vote on deals, discounts and coupons from different branches.
\newline

In the article "Enhanced query processing over semantic cache for cloud based relational databases" \cite{Ahmad:2020} published in April 2020,  the authors proposed the approach for improving the hit rate of the cache system by using an implicit semantic matching algorithm that involves four different scenarios, where each is designed to optimize the cache hit rate based on the query predicate and attribute matching. Furthermore they evaluated different experiments, which showed that it outperformed existing techniques in terms of time complexity and hit rate. The experiments were conducted on a prototype system that included a database management system and were cache maintained on the same device.
\newline

The paper "Integrated Environment Based on Anytime Solution Search Algorithms and A Non-Relational Database for Real-Time Intelligent Systems" \cite{Eremeeva:2020} describes an integrated environment for real-time intelligent systems that uses anytime solution search algorithms and a non-relational database. The use of anytime algorithms and NoSQL databases improves efficiency when working with graph-based and speeds up the process of obtaining a solution.
\newline

The article "BANKS: Browsing and Keyword Searching in Relational Databases" \cite{Aditya:2007}, discusses Browsing And Keyword Searching (BANKS), which allows for easy publishing of relational and XML data on the web. Relational database management systems require knowledge of schema and query language for a query that is used to get specific information from a database when the need arises, which makes it difficult for casual users to make search requests. An alternative would be an HTML form, where the users can use predefined queries, but creating forms for each task is laborious and confusing. The best solution would be to create Search engines on the web, that offers a simpler alternative through unstructured querying and browsing using keywords and hyperlinks. Keyword search can provide a user-friendly mechanism for casual users to access database information without requiring schema knowledge.